### 2022-07-03 Papers/ICCC-2023/sections/abstract.tex
added bibliography

CTFE first pattern is design with compiling low-level, non-garbage-collected, reflection-enabled languages in mind.
It was created in order to compile C-=-1, which aimed to allow the programmer to execute any code at compile time, as well as anylyze and modify the program structure.
Thanks to the extensibility of the designed compiler, programs written in C-=-1 can also generate marshalling bindings for other languages and support a variety of unexpected programming paradigms.

>>>>

CTFE first pattern is designed with compiling low-level, non-garbage-collected, reflection-enabled languages in mind.
It was created in order to compile C-=-1, which aimed to allow the programmer to execute any code at compile time, as well as analyze and modify the program structure.
Thanks to the extensibility of the designed compiler, programs written in C-=-1 can also generate marshalling bindings for other languages and support a variety of unexpected programming paradigms.
